Growth of the South African Economy:\\An Empirical Evaluation

### 2014-07-09 Article_JAE_2014/ZAGrowth_JAE.Rnw
Now using nestStr and nestStrParen where appropriate.

<<CD_GDP_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=5, fig.height=3, fig.cap="Cobb-Douglas fitted models.">>=
cdFittedData_ZA <- filter(fitted_df_ZA, model=="cd", nest %in% c("iK+iL", "iK+iL+iQ"))
spaghettiPlot(data=cdFittedData_ZA, facet_formula=Country~energy, level=spaghettiGraphLevel) +
    labs(y="Indexed GDP (1991=1)")
@

@@

<<CES_lambda_theta_graph, fig.pos="H", fig.align='center', fig.width=5, fig.height=3, fig.cap="$\\lambda$ and $\\theta$ values for CES resample models with various nestings.">>=
cesCoeffsData_ZA <- filter(coeffs_df_ZA, model=="ces", nestStr %in% c("iK+iL", "iK+iL+iQ", "iL+iQ+iK", "iQ+iK+iL"))
standardScatterPlot(data=cesCoeffsData_ZA, mapping=aes(gamma_coef, lambda), facet_formula=country~nest, alpha=0.05) +
    scale_x_continuous(breaks=c(0.95, 1.0, 1.05)) +
    scale_y_continuous(breaks=c(0, 0.002, 0.004, 0.006, 0.008)) +    
    labs(x=expression(theta), y=expression(lambda))
@

<<CES_sigma1_delta1_graph, fig.pos="H", fig.align='center', fig.width=5, fig.height=3, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models with various nestings.">>=
standardScatterPlot(data=cesCoeffsData_ZA, mapping=aes(delta_1, sigma_1), facet_formula=country~nest, alpha=0.05) +
    coord_trans(y="sigma") +
    scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    labs(x=expression(delta[1]), y=expression(sigma[1]))
@

<<CES_sigma_delta_graph, fig.pos="H", fig.align='center', fig.width=5, fig.height=3, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models with various nestings.">>=
standardScatterPlot(data=subset(cesCoeffsData_ZA, nestStr != "iK+iL"),
                    mapping=aes(delta, sigma), facet_formula=country~nest, alpha=0.05) +
    coord_trans(y="sigma") +
    scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    labs(x=expression(delta), y=expression(sigma))
@

@@

<<CES_ternary_graph, fig.pos="H", fig.align='center', fig.width=5, fig.height=3, fig.cap="$\\alpha$, $\\beta$, and $\\gamma$ values for CES resample models with various nestings.">>=
standardTriPlot(data=cesCoeffsData_ZA, facet_formula=country~nest)
@

<<CES_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=5, fig.height=3, fig.cap="CES fitted models with various nestings.">>=
cesFittedData_ZA <- filter(fitted_df_ZA, model=="ces", nest %in% c("iK+iL", "iK+iL+iQ", "iL+iQ+iK", "iQ+iK+iL"))
spaghettiPlot(data=cesFittedData_ZA, facet_formula=Country~nest, level=spaghettiGraphLevel) +
    labs(y="Indexed GDP (1991=1)")
@

>>>>

<<CD_GDP_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=5, fig.height=3, fig.cap="Cobb-Douglas fitted models.">>=
cdFittedData_ZA <- filter(fitted_df_ZA, model=="cd", nestStr %in% c("iK+iL", "iK+iL+iQ"))
spaghettiPlot(data=cdFittedData_ZA, facet_formula=Country~energy, level=spaghettiGraphLevel) +
    labs(y="Indexed GDP (1991=1)")
@

@@

<<CES_lambda_theta_graph, fig.pos="H", fig.align='center', fig.width=5, fig.height=3, fig.cap="$\\lambda$ and $\\theta$ values for CES resample models with various nestings.">>=
cesCoeffsData_ZA <- filter(coeffs_df_ZA, model=="ces", nestStr %in% c("iK+iL", "iK+iL+iQ", "iL+iQ+iK", "iQ+iK+iL"))
standardScatterPlot(data=cesCoeffsData_ZA, mapping=aes(gamma_coef, lambda), 
    facet_formula=country~nestStrParen, alpha=0.05) +
    scale_x_continuous(breaks=c(0.95, 1.0, 1.05)) +
    scale_y_continuous(breaks=c(0, 0.002, 0.004, 0.006, 0.008)) +    
    labs(x=expression(theta), y=expression(lambda))
@

<<CES_sigma1_delta1_graph, fig.pos="H", fig.align='center', fig.width=5, fig.height=3, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models with various nestings.">>=
standardScatterPlot(data=cesCoeffsData_ZA, mapping=aes(delta_1, sigma_1), 
    facet_formula=country~nestStrParen, alpha=0.05) +
    coord_trans(y="sigma") +
    scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    labs(x=expression(delta[1]), y=expression(sigma[1]))
@

<<CES_sigma_delta_graph, fig.pos="H", fig.align='center', fig.width=5, fig.height=3, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models with various nestings.">>=
standardScatterPlot(data=subset(cesCoeffsData_ZA, nestStr != "iK+iL"),
                    mapping=aes(delta, sigma), facet_formula=country~nestStrParen, alpha=0.05) +
    coord_trans(y="sigma") +
    scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    labs(x=expression(delta), y=expression(sigma))
@

@@

<<CES_ternary_graph, fig.pos="H", fig.align='center', fig.width=5, fig.height=3, fig.cap="$\\alpha$, $\\beta$, and $\\gamma$ values for CES resample models with various nestings.">>=
standardTriPlot(data=cesCoeffsData_ZA, facet_formula=country~nestStrParen)
@

<<CES_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=5, fig.height=3, fig.cap="CES fitted models with various nestings.">>=
cesFittedData_ZA <- filter(fitted_df_ZA, model=="ces", nestStr %in% c("iK+iL", "iK+iL+iQ", "iL+iQ+iK", "iQ+iK+iL"))
spaghettiPlot(data=cesFittedData_ZA, facet_formula=Country~nestStrParen, level=spaghettiGraphLevel) +
    labs(y="Indexed GDP (1991=1)")
@
